Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
More new results
#imtired

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \medskip
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation} & \textbf{\#} & \textbf{\%} \\ \hline
Unrelated          & 4,762 & 38.14            \\ \hline
Same Class          & 3,131 & 25.07             \\ \hline
Sibling               & 1,949 & 15.61            \\ \hline
Same Method         & 1,685 & 13.49             \\ \hline
External Superclass   & 558 & 4.47             \\ \hline
First Cousin          & 197 & 1.58           \\ \hline
Superclass          & 118 & 0.94           \\ \hline
Common Hierarchy    & 73 & 0.58            \\ \hline
Ancestor          & 14 & 0.11          \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations} \label{table:locations}
  \medskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location}   & \textbf{\#} & \textbf{\%} \\ \hline
Method Level        & 19,075 & 58.23            \\ \hline
Class Level        & 12,207 & 37.27            \\ \hline
Constructor Level    & 1,080 & 3.30           \\ \hline
Interface Level   & 247 & 0.75           \\ \hline
Enum Level         & 147 & 0.45            \\ \hline
\end{tabular}
\end{center}
\end{table}

Our results indicate that around 58\% of the clones are produced at method-level. About 39\% of clones either span several methods/constructors or contain something like a field declaration. Another 3\% of the clones are found in constructors. The amount of clones found in interfaces and enumerations is very low. Regarding the differences between type 1 and T1R, it seems that there are relatively less method level clones and more class level clones for T1R. This is probably due to that the main reason for variability between type 1 and T1R is variable references, which occur more at method level than class level.

>>>>

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \medskip
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation} & \textbf{\#} & \textbf{\%} \\ \hline
Unrelated          & 12,368 & 34.88            \\ \hline
Same Class          & 11,483 & 32.38             \\ \hline
Same Method               & 5,056 & 14.26            \\ \hline
Sibling         & 4,182 & 11.79             \\ \hline
External Superclass   & 1,066 & 3.01             \\ \hline
Superclass          & 558 & 1.57           \\ \hline
First Cousin          & 489 & 1.38           \\ \hline
Common Hierarchy    & 206 & 0.58            \\ \hline
Ancestor          & 54 & 0.15          \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations} \label{table:locations}
  \medskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location}   & \textbf{\#} & \textbf{\%} \\ \hline
Method Level        & 83,813 & 82.62            \\ \hline
Class Level        & 12,534 & 12.35            \\ \hline
Constructor Level    & 4,391 & 4.33           \\ \hline
Interface Level   & 567 & 0.56           \\ \hline
Enum Level         & 145 & 0.14            \\ \hline
\end{tabular}
\end{center}
\end{table}

Our results indicate that, quite significantly, most clones are found at method level. The amount of clones found in interfaces and enumerations is very low.
